Reducing iptables configuration complexity using chains

### 2014-03-27 iptables_newline2014/presentation.tex
add RELATED state
add setup and summary

      iptables -A OUTPUT -m state --state ESTABLISHED -j ACCEPT}

@@

>>>>

      iptables -A OUTPUT -m state --state ESTABLISHED,RELATED -j ACCEPT}

@@

    \frametitle{Realworld example : setup}
      \item Tcp port 80 (http) and 443 (https) is available for all.
      \item ssh (port 20) and webmin (port 10000), is limited to admin PCs.
      \item A SMB service is limited to admin and webmaster PCs.
      \item Some outgoing connections are allowed (dns, dhcp, smtp, ntp).
      \item Some external websites are reachable.
    \frametitle{Summary}
      \item use ESTABLISHED state to reduce number of rules
      \item using chains makes your rules easier readable and maintainable
      \item chains can be reused for several rules
      \item chains can be chained together
      \item faster, because it only jumps to a chain when a rule matches
